NumPy---Array Computation for Python

### 2019-12-19 paper.tex
Move project organization section

@@

\section*{Common infrastructure}

In addition to the testing and building packages described above,
as the fundamental package for numerical and scientific computing
in Python, NumPy also plays a central role in building and
standardizing much of the community infrastructure.
The docstring standard mentioned in the history section is now
widely adopted.
We are also using the NEP system as a way to help coordinate
the larger scientific Python community.
% https://numpy.org/neps/nep-0029-deprecation_policy.html
For example, in NEP 29, we recommend, along with leaders from various other
projects, that all projects across the Scientific Python ecosystem adopt a
common ``time window-based'' policy for support of Python and NumPy versions.
This standard will simplify downstream project and release planning.

\subsection*{Wheels build system}

A Python \emph{wheel}\cite{PEP427} is a standard file format for
distributing Python libraries.  In addition to Python code, a
wheel may include compiled C extensions and other binary data.
This is important, because many libraries, including NumPy,
require a C compiler and other build tools to build the software
from the source code, making it difficult for many users to install
the software on their own.  The introduction of wheels to the Python
packaging system has made it much easier for users to install
precompiled libraries.

A GitHub repository containing scripts to build NumPy wheels has
been configured so that a simple commit to the repository triggers
an automated build system that creates NumPy wheels for several
computer platforms, including Windows, Mac OSX and Linux.  The wheels
are uploaded to a public server and made available for anyone to use.
This system makes it easy for users to install precompiled versions
of NumPy on these platforms.

The technology that is used to build the wheels evolves continually.
At the time this paper is being written, a key component is the
\code{multibuild} suite of tools developed by Matthew Brett and
other developers\cite{multibuild}.  Currently, scripts using
\code{multibuild} are written for the continuous integration
platforms Travis-CI (for Linux and Mac OSX) and Appveyor
(for Windows).

>>>>

NumPy plays a central role in building and standardizing much of the scientific
Python community infrastructure.
The docstring standard mentioned in the history section is now widely adopted.
We are also using the NEP system as a way to help coordinate the larger
scientific Python community.
% https://numpy.org/neps/nep-0029-deprecation_policy.html
For example, in NEP 29, we recommend, along with leaders from various other
projects, that all projects across the Scientific Python ecosystem adopt a
common ``time window-based'' policy for support of Python and NumPy versions.
This standard will simplify downstream project and release planning.

@@

% \section*{Common infrastructure}

%\subsection*{Wheels build system}
%
%A Python \emph{wheel}\cite{PEP427} is a standard file format for
%distributing Python libraries.  In addition to Python code, a
%wheel may include compiled C extensions and other binary data.
%This is important, because many libraries, including NumPy,
%require a C compiler and other build tools to build the software
%from the source code, making it difficult for many users to install
%the software on their own.  The introduction of wheels to the Python
%packaging system has made it much easier for users to install
%precompiled libraries.
%
%A GitHub repository containing scripts to build NumPy wheels has
%been configured so that a simple commit to the repository triggers
%an automated build system that creates NumPy wheels for several
%computer platforms, including Windows, Mac OSX and Linux.  The wheels
%are uploaded to a public server and made available for anyone to use.
%This system makes it easy for users to install precompiled versions
%of NumPy on these platforms.
%
%The technology that is used to build the wheels evolves continually.
%At the time this paper is being written, a key component is the
%\code{multibuild} suite of tools developed by Matthew Brett and
%other developers\cite{multibuild}.  Currently, scripts using
%\code{multibuild} are written for the continuous integration
%platforms Travis-CI (for Linux and Mac OSX) and Appveyor
%(for Windows).
